# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
Para cargar los datos
```{r echo:true}
# Cargamos los datos originales
data <- read.csv("/Users/gaspar/Dropbox/Cursos/Coursera/ReproducibleResearch/Assessment1/RepData_PeerAssessment1/activity.csv", header=TRUE, fill=TRUE, na.strings="NA")
summary(data)
```
## What is mean total number of steps taken per day?
### Histogram of the total number of steps taken each day
```{r}
temp <- aggregate(data$steps, list(data$date), FUN=sum)
hist(temp$x)
```
### Calculate and report the mean and median total number of steps taken per day
```{r}
meanSteps <- aggregate(data$steps, list(data$date), FUN=mean)
summary(temp)
```
## What is the average daily activity pattern?
### Time series plot
```{r}
plot(temp$x, type = "o")
plot(data$steps, type = "l")
```
### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

## Imputing missing values
### Calculate and report the total number of missing values in the dataset
```{r}
summary(data)
```
The total numner of missing values in the data set is 2304.
### Filling in all of the missing values in the dataset
```{r}

```
## Are there differences in activity patterns between weekdays and weekends?
